---
title: "Study 1"
author: "Evan Valdes"
date: "7/17/2020"
output:
  html_document: default
  pdf_document: default
---

```{r}
## Set working directory----
setwd("/Users/Evanvaldes1/Desktop/MASSEY/STUDY 1")
```

```{r}
library(dplyr)
library(surveydata)
library(Hmisc)
library(ggplot2)
library(psych)
library(haven)
library(stats)
library(lavaan)
library(semPlot)
library(semTools)
library(PerformanceAnalytics)
library(ggiraphExtra)
library(equaltestMI)
library(stargazer)
library(sjPlot)
library(apaTables)
library(jtools)
library(pwr)
library(effsize)
library(nlme)
library(interplot)
library(ggthemes)
library(cowplot)
library(officer)
library(tidyverse)
library(ltm)
library(mice)
library(styler)
library(BaylorEdPsych)
library(mitools)
```

```{r}
## Load data----
D1_CHINA_AND_USA <- read_sav("D1 CHINA AND USA.sav")
```

## A PRIORI POWER ANALYSIS 
```{r}

r_power_CHINA <- pwr.f2.test(u = 5, v = NULL, f2 = 0.02, sig.level = .05, power = .8)

r_power_CHINA

r_power_USA <- pwr.f2.test(u = 5, v = NULL, f2 = 0.02, sig.level = .05, power = .8)

r_power_USA

```

```{r}
## Changing class of variables to numeric ----
#MW: This is totally fine but there can be more efficient ways to make changes to many variables at once. A couple of tricks:
#grep allows you to pull out matching patterns.
#sapply allows you to apply a function (e.g., as_numeric) to multiple vectors all at once

#Eg. the two lines below convert all the items starting wiht "SJ" to numeric. 
SJ_vars = grep("SJ", names(D1_CHINA_AND_USA), value = TRUE)
D1_CHINA_AND_USA[,SJ_vars] = sapply(D1_CHINA_AND_USA[,SJ_vars], as.numeric)


D1_CHINA_AND_USA$SJ <- as.numeric(D1_CHINA_AND_USA$SJ)
D1_CHINA_AND_USA$SJ1 <- as.numeric(D1_CHINA_AND_USA$SJ1)
D1_CHINA_AND_USA$SJ2 <- as.numeric(D1_CHINA_AND_USA$SJ2)
D1_CHINA_AND_USA$SJ3 <- as.numeric(D1_CHINA_AND_USA$SJ3) 
D1_CHINA_AND_USA$SJ4 <- as.numeric(D1_CHINA_AND_USA$SJ4)
D1_CHINA_AND_USA$SJ_W2 <- as.numeric(D1_CHINA_AND_USA$SJ_W2)
D1_CHINA_AND_USA$SJ1_W2 <- as.numeric(D1_CHINA_AND_USA$SJ1_W2)
D1_CHINA_AND_USA$SJ2_W2 <- as.numeric(D1_CHINA_AND_USA$SJ2_W2)
D1_CHINA_AND_USA$SJ3_W2 <- as.numeric(D1_CHINA_AND_USA$SJ3_W2)
D1_CHINA_AND_USA$SJ4_W2 <- as.numeric(D1_CHINA_AND_USA$SJ4_W2)
D1_CHINA_AND_USA$AmericaThreat <- as.numeric(D1_CHINA_AND_USA$AmericaThreat)
D1_CHINA_AND_USA$Social_Status <- as.numeric(D1_CHINA_AND_USA$Social_Status)
D1_CHINA_AND_USA$Social_Status_W2 <- as.numeric(D1_CHINA_AND_USA$Social_Status_W2)
D1_CHINA_AND_USA$Trust_USA <- as.numeric(D1_CHINA_AND_USA$Trust_USA)
D1_CHINA_AND_USA$Trust_USA_W2 <- as.numeric(D1_CHINA_AND_USA$Trust_USA_W2)
D1_CHINA_AND_USA$Trust_Russia_W2 <- as.numeric(D1_CHINA_AND_USA$Trust_Russia_W2)
D1_CHINA_AND_USA$Eduaction_L1 <- as.numeric(D1_CHINA_AND_USA$Eduaction_L1)
D1_CHINA_AND_USA$Trust_LocGvt <- as.numeric(D1_CHINA_AND_USA$Trust_LocGvt)
D1_CHINA_AND_USA$Trust_LocGvt_W2 <- as.numeric(D1_CHINA_AND_USA$Trust_LocGvt_W2)
D1_CHINA_AND_USA$TrustGen <- as.numeric(D1_CHINA_AND_USA$TrustGen)
D1_CHINA_AND_USA$House_Income <- as.numeric(D1_CHINA_AND_USA$House_Income)
D1_CHINA_AND_USA$House_Income_2 <- as.numeric(D1_CHINA_AND_USA$House_Income_2)
D1_CHINA_AND_USA$Trust_China_W2 <- as.numeric(D1_CHINA_AND_USA$Trust_China_W2)
D1_CHINA_AND_USA$Trust_NatGvt <- as.numeric(D1_CHINA_AND_USA$Trust_NatGvt)
D1_CHINA_AND_USA$Trust_NatGvt_W2 <- as.numeric(D1_CHINA_AND_USA$Trust_NatGvt_W2)
D1_CHINA_AND_USA$Trust_Judiciary <- as.numeric(D1_CHINA_AND_USA$Trust_Judiciary)
D1_CHINA_AND_USA$Trust_Judiciary_W2 <- as.numeric(D1_CHINA_AND_USA$Trust_Judiciary_W2)
D1_CHINA_AND_USA$LibCon_Economic <- as.numeric(D1_CHINA_AND_USA$LibCon_Economic)
D1_CHINA_AND_USA$LibCon_Economic_W2 <- as.numeric(D1_CHINA_AND_USA$LibCon_Economic_W2)
D1_CHINA_AND_USA$LibCon_Political <- as.numeric(D1_CHINA_AND_USA$LibCon_Political)
D1_CHINA_AND_USA$LibCon_Political_W2 <- as.numeric(D1_CHINA_AND_USA$LibCon_Political_W2)
D1_CHINA_AND_USA$LibCon_Social <- as.numeric(D1_CHINA_AND_USA$LibCon_Social)
D1_CHINA_AND_USA$LibCon_Social_W2 <- as.numeric(D1_CHINA_AND_USA$LibCon_Social_W2)
D1_CHINA_AND_USA$Age <- as.numeric(D1_CHINA_AND_USA$Age)
D1_CHINA_AND_USA$Age_W2 <- as.numeric(D1_CHINA_AND_USA$Age_W2)
D1_CHINA_AND_USA$Gender <- as.numeric(D1_CHINA_AND_USA$Gender)
D1_CHINA_AND_USA$RWA <- as.numeric(D1_CHINA_AND_USA$RWA)
D1_CHINA_AND_USA$Country <- as.numeric(D1_CHINA_AND_USA$Country)

```

## Centering variables for regression analyses
```{r}
mean(D1_CHINA_AND_USA$SJ,na.rm = T )
mean(D1_CHINA_AND_USA$SJ_W2, na.rm = T)
mean(D1_CHINA_AND_USA$Eduaction_L1, na.rm = T)
mean(D1_CHINA_AND_USA$Social_Status, na.rm = T)
mean(D1_CHINA_AND_USA$Age, na.rm = T)


D1_CHINA_AND_USA$SJ <- (D1_CHINA_AND_USA$SJ - 3.796506)
D1_CHINA_AND_USA$SJ_W2 <- (D1_CHINA_AND_USA$SJ_W2 - 3.87419)
D1_CHINA_AND_USA$Eduaction_L1 <- (D1_CHINA_AND_USA$Eduaction_L1 - 3.951973)
D1_CHINA_AND_USA$Social_Status <- (D1_CHINA_AND_USA$Social_Status - 5.267965)
D1_CHINA_AND_USA$Age <- (D1_CHINA_AND_USA$Age - 44.5947)
```

## Recoding Country values - china = 0 USA = 1
```{r}
## Changing Country names ----
D1_CHINA_AND_USA$Country2 <- NA

D1_CHINA_AND_USA$Country2[D1_CHINA_AND_USA$Country == "4"] <- "0"
D1_CHINA_AND_USA$Country2[D1_CHINA_AND_USA$Country == "22"] <- "1"

D1_CHINA_AND_USA$Country2 <- as.numeric(D1_CHINA_AND_USA$Country2)

D1_CHINA_AND_USA$Country2 <- gsub("0", "China", D1_CHINA_AND_USA$Country2)
D1_CHINA_AND_USA$Country2 <- gsub("1", "USA", D1_CHINA_AND_USA$Country2)

```



```{R}
## Making Country a factor
D1_CHINA_AND_USA$Country2 <- as.factor(D1_CHINA_AND_USA$Country2)

## Dragging participant age from wave 1

D1_CHINA_AND_USA <- D1_CHINA_AND_USA %>% mutate(
  Age_W2 = 
    dplyr::coalesce(
      Age
    )
)
```

## Transforming income variable to 0 - 100% 
```{r}
D1_CHINA_AND_USA$income_percent = NA


D1_CHINA_AND_USA$income_percent <- rank(D1_CHINA_AND_USA$House_Income)/length(D1_CHINA_AND_USA$House_Income)*100
```

```{r}
Incomedata <- subset(D1_CHINA_AND_USA, select = c(
  "Country2", "House_Income", "income_percent",
  "Eduaction_L1", "SJ", "SJ_W2",
  "Social_Status", "Age", "Age_W2", "Gender",
  "SJ1", "SJ2", "SJ3", "SJ4", "RWA", "LibCon_Economic",
  "LibCon_Political", "LibCon_Social"
))
```

## Missing data analysis
```{r}
colSums(is.na(Incomedata))
```

## Calculating percentage of missing data for analyses
```{r}
totalcells <- prod(dim(Incomedata))
missingcells <- sum(is.na(Incomedata))
percentage <- (missingcells *100)/(totalcells)

percentage
```

## Multiple imputation of NA values using mice package
```{r}
md.pattern(Incomedata)
```

## linear regression using bootstrap from mice package for multiple imputation
## Number of imputations (m = 40) using White et al. (2011) practical rule 
## of thumb that m should be at least equal to % of incomplete cases
```{r}
## Impute data function
imputed_data <- mice(Incomedata, m=40, method = "norm.boot", seed = 100)
summary(imputed_data)

options(scipen = 999)

## pooling imputed data to fit model waves 1 and 2
fit1 <- with(data = imputed_data, exp = lm(SJ ~ Age + Gender + Country2 + Eduaction_L1 + income_percent
                      + Social_Status + Age*Country2 + Gender*Country2 +
                        Eduaction_L1*Country2 + income_percent*Country2 + 
                        Social_Status*Country2))

fit2 <- with(data = imputed_data, exp = lm(SJ_W2 ~ Age + Gender + Country2 + Eduaction_L1 + income_percent
                     + Social_Status + SJ + Age*Country2
                     + Gender*Country2 + Eduaction_L1*Country2 + 
                       income_percent*Country2 + Social_Status*Country2 + 
                        SJ*Country2))

## Single SJ item analysis used by Li et al.
fit3 <- with(data = imputed_data, exp = lm(SJ1 ~ Age + Gender + Country2 + Eduaction_L1 + income_percent +
  Social_Status + Age * Country2 + Gender * Country2 + Eduaction_L1 * Country2 +
  income_percent * Country2 + Social_Status * Country2))

summary(pool(fit1))
pool.r.squared(fit1)

summary(pool(fit2))
pool.r.squared(fit2)

summary(pool(fit3))
pool.r.squared(fit3)


## Reviewer 2 requested analysis (Comment 4)
fit4 <- with(data = imputed_data, exp = lm(SJ ~ income_percent + Eduaction_L1 + Social_Status + income_percent*Social_Status + Eduaction_L1*Social_Status))

summary(pool(fit4))
pool.r.squared(fit4)
```

## Comparing pooled results of MI
```{r}
stacked_imputed_data <- complete(imputed_data, "long", include = T)
finished_imputed_data <- complete(imputed_data, 4)

```

## Cronbachs Alpha using ltm package
```{r}

data <- subset(finished_imputed_data, select = c(SJ1, SJ2, SJ3, SJ4))
cronbach.alpha(data,
  standardized = F, CI = F, probs = c(0.025, 0.975), B = 1000,
  na.rm = T
)

```


## Testing Measurement invariance 
```{r}

## Simple CFA of SJ loading onto its 4 variables Wave 1

SJSESCFA <- 'SYSJ =~ SJ1 + SJ2 + SJ3 + SJ4
OSES =~ income_percent + Eduaction_L1
SSES =~ Social_Status'

# configural invariance (does the model seem to fit the data reasonably well in both countries?)
fit1 <- cfa.mi(SJSESCFA, data = imputed_data, group = "Country2")

summary(fit1, standardized = TRUE, rsquare = TRUE, fit.measures = TRUE)


# weak invariance/metric invariance (are the relationships between the latent variable SJ and the items about the same in both countries? This is probably the main thing that matters for us)

fit2 <- cfa.mi(SJSESCFA, data = imputed_data, group = "Country2",

            group.equal = "loadings")
summary(fit2, standardized = TRUE, rsquare = TRUE, fit.measures = TRUE)

 

# strong invariance (are the intercepts the same in both countries? This would need to hold to compare mean differences across countries, probably less important for us)

fit3 <- cfa.mi(SJSESCFA, data = imputed_data, group = "Country2",

            group.equal = c("intercepts", "loadings"))
summary(fit3, standardized = TRUE, rsquare = TRUE, fit.measures = TRUE)

 

# model comparison tests (comparison to fit1 to fit2 is the main thing that establishes weak invariance).

lavTestLRT.mi(fit1, test = "D2", pool.robust = T)
lavTestLRT.mi(fit2, test = "D2", pool.robust = T)
lavTestLRT.mi(fit3, test = "D2", pool.robust = T)
```

## Path Diagram for simple CFA


## Correlation analysis per country - subset each country
## Creating subset for China and USA
```{r}
smallchina <- filter(finished_imputed_data, Country2 == "China")

smallusa <- filter(finished_imputed_data, Country2 == "USA")
```

## China Correlation
```{r}
chinasubset <- subset(smallchina, select = c(SJ, SJ_W2, Social_Status, Eduaction_L1, income_percent, Age, Gender))

chart.Correlation(chinasubset, histogram = TRUE, pch = 19)

apa.cor.table(chinasubset, filename = "chinacortable1.doc", table.number = 1)

```

## USA Correlation
```{r}
usasubset <- subset(smallusa, select = c(
  SJ, SJ_W2, Social_Status, Eduaction_L1, income_percent, Age, Gender
))

chart.Correlation(usasubset, histogram = TRUE, pch = 19)

apa.cor.table(usasubset, filename = "usacortable1.doc", table.number = 2)

```


## Centering variables for regression analyses
```{r}
mean(finished_imputed_data$SJ)
mean(finished_imputed_data$SJ_W2)
mean(finished_imputed_data$Eduaction_L1)
mean(finished_imputed_data$Social_Status)
mean(finished_imputed_data$Age)


finished_imputed_data$SJ <- (finished_imputed_data$SJ - 3.796852)
finished_imputed_data$SJ_W2 <- (finished_imputed_data$SJ_W2 - 3.84396)
finished_imputed_data$Eduaction_L1 <- (finished_imputed_data$Eduaction_L1 - 3.831144)
finished_imputed_data$Social_Status <- (finished_imputed_data$Social_Status - 5.271802)
finished_imputed_data$Age <- (finished_imputed_data$Age - 44.67253)
```

```{r}

# regression model with the full sample with interaction terms 

fullregression <- lm(SJ_W2 ~ Age + Gender + Country2 + Eduaction_L1 + income_percent
                     + Social_Status + SJ + Age*Country2
                     + Gender*Country2 + Eduaction_L1*Country2 + 
                       income_percent*Country2 + Social_Status*Country2 + 
                        SJ*Country2,
                     data = finished_imputed_data
                       )

summary(fullregression)
anova(fullregression)

```

## Interaction plots for wave 2

## Interaction of education

```{r}
 p1 <- interplot(m = fullregression, var1 = "Eduaction_L1", var2 = "Country2") +
  xlab("Country, 0 = China, 1 = USA") + ylab("Estimated Interaction of Objective SES (Education)") + geom_hline(yintercept = 0, linetype = "dashed") + 
  theme_apa(x.font.size = 7, y.font.size = 7)

```
## Interaction of income
```{r}
p2 <- interplot(m = fullregression, var1 = "income_percent", var2 = "Country2") +
  xlab("Country, 0 = China, 1 = USA") + ylab("Estimated Interaction of Objective SES (Income)") + geom_hline(yintercept = 0, linetype = "dashed") + 
  theme_apa(x.font.size = 7, y.font.size = 7)

```
## Interaction of Social Status
```{r}
  p3 <- interplot(m = fullregression, var1 = "Social_Status", var2 = "Country2") +
  xlab("Country, 0 = China, 1 = USA") + ylab("Estimated interaction of Subjective SES (Wave 1)") +
  geom_hline(yintercept = 0, linetype = "dashed") + 
  theme_apa(x.font.size = 7, y.font.size = 7)

```


## Creating plot grid of wave two effect
```{r}
title <- ggdraw() +
  draw_label("Conditional Coefficient of Subjective and Objective SES on SJ by Country", fontface = "bold", x = 0, hjust = 0)
plot_row <- plot_grid(p1, p2, p3)
wave_2_effect_plot <- plot_grid(title, plot_row, ncol = 1, rel_heights = c(0.1, 1))
ggsave("wave2_image.png", wave_2_effect_plot)
```
## converting plots to word doc format wave 2
```{r}
wave2_effect_plot_doc <- read_docx()
wave2_effect_plot_doc <- body_add_img(wave2_effect_plot_doc, src = "wave2_image.png", width = 7, height = 7)
print(wave2_effect_plot_doc, target = "wave2_effect_plot_doc.docx")
```

```{r}
## Wave 1 regression model with full sample and interaction termS


fullregression2 <- lm(SJ ~ Age + Gender + Country2 + Eduaction_L1 + income_percent
                      + Social_Status + Age*Country2 + Gender*Country2 +
                        Eduaction_L1*Country2 + income_percent*Country2 + 
                        Social_Status*Country2, data = finished_imputed_data)

summary(fullregression2)
anova(fullregression2)

```

## Interaction plots for wave 1

## Interaction plot for Education
```{r}
p4 <- interplot(m = fullregression2, var1 = "Eduaction_L1", var2 = "Country2") + 
  xlab("Country, 0 = China, 1 = USA") + ylab("Estimated interaction of Objective SES (Education)") +
  geom_hline(yintercept = 0, linetype = "dashed") + theme_apa(x.font.size = 7, y.font.size = 7)

```

```{r}
p5 <- interplot(m = fullregression2, var1 = "income_percent", var2 = "Country2") + 
  xlab("Country, 0 = China, 1 = USA") + ylab("Estimated interaction of Objective SES (Income)") + 
  geom_hline(yintercept = 0, linetype = "dashed") + theme_apa(x.font.size = 7, y.font.size = 7)
```

```{r}
p6 <- interplot(m = fullregression2, var1 = "Social_Status", var2 = "Country2") +
  xlab("Country, 0 = China, 1 = USA") + ylab("Estimated interaction of Subjective SES (Wave 1)") +
  geom_hline(yintercept = 0, linetype = "dashed") + 
  theme_apa(x.font.size = 7, y.font.size = 7)
```

## Creating multiple plots in one
```{r}
title1 <- ggdraw() + 
draw_label("Conditional Coefficient of Subjective and Objective SES on SJ by Country", fontface = 'bold', x = 0, hjust = 0) 
plot_row <- plot_grid(p4, p5, p6)
wave_1_effect_plot <- plot_grid(title1, plot_row, ncol = 1, rel_heights = c(0.1, 1))
ggsave("wave1_image.png", wave_1_effect_plot)
```
## converting plots to word doc format wave 1
```{r}
wave1_effect_plot_doc <- read_docx()
wave1_effect_plot_doc <- body_add_img(wave1_effect_plot_doc, src = "wave1_image.png", width = 7, height = 7)
print(wave1_effect_plot_doc, target = "wave1_effect_plot_doc.docx")
```

## LM tables for paper - China Vs USA - WAVE 1 and 2
```{r}

stargazer(fullregression2, fullregression, no.space = T, dep.var.labels = c("System Justification Wave 1", "System Justification Wave 2"), ci = T, ci.level = 0.95,  type = "html", digits = 2, out = "Wave_1&2_LM.doc")
```

```{r}
## Creating a descriptives table 1----
## Only run after running correlation tables
## and regressions or you will get an error 
## when trying to run. Skip if you are changing 
## gender names below
#MW: This seems to go fine with the code run in the order it's presented.
library(table1)
finished_imputed_data$Gender <- factor(finished_imputed_data$Gender, levels = c(1, 0),
                                  labels = c("Male",
                                             "Female"))
label(finished_imputed_data$Age) <- "Age"
label(finished_imputed_data$Gender) <- "Gender"


table1::table1(~Age + Gender | Country2, data = finished_imputed_data)
```

## SENSITIVITY POWER ANALYSIS
```{r}
smallchina <- filter(Incomedata, Country2 == "China")
smallusa <- filter(Incomedata, Country2 == "USA")
colSums(is.na(smallchina))
colSums(is.na(smallusa))

r_power_CHINA <- pwr.f2.test(u = 5, v = NULL, f2 = 0.02, sig.level = .05, power = .8)

r_power_CHINA

r_power_USA <- pwr.f2.test(u = 5, v = NULL, f2 = 0.02, sig.level = .05, power = .8)

r_power_USA
```

## Using single SJ item as Li et al
## running on cross-sectional data
```{r}
regression2 <- lm(SJ1 ~ Age + Gender + Country2 + Eduaction_L1 + income_percent +
                    Social_Status + Age*Country2 + Gender*Country2 + Eduaction_L1*Country2 +
                    income_percent*Country2 + Social_Status*Country2, data = finished_imputed_data)

summary(regression2)
anova(regression2)
```


```{r}
interplot(m = regression2, var1 = "Social_Status", var2 = "Country2") +
        xlab("Country, 0 = China, 1 = USA") + ylab("Estimated interaction of Subjective SES") +
        geom_hline(yintercept = 0, linetype = "dashed") + 
        theme_apa(x.font.size = 7, y.font.size = 7)

interplot(m = regression2, var1 = "income_percent", var2 = "Country2") +
  xlab("Country, 0 = China, 1 = USA") + ylab("Estimated interaction of Objective SES (income)") +
  geom_hline(yintercept = 0, linetype = "dashed") + 
  theme_apa(x.font.size = 7, y.font.size = 7)

interplot(m = regression2, var1 = "Eduaction_L1", var2 = "Country2") +
  xlab("Country, 0 = China, 1 = USA") + ylab("Estimated interaction of Objective SES (education)") +
  geom_hline(yintercept = 0, linetype = "dashed") + 
  theme_apa(x.font.size = 7, y.font.size = 7)
```

## Added analyses

## Descriptive stats of variables of interest
## Adding Median and Range to correlation tables
```{r}
summarystat <- subset(finished_imputed_data, select = c("Country2","SJ", "SJ_W2" ,"Gender", "Age", "Eduaction_L1", "income_percent", "Social_Status"))

describeBy(summarystat, group = summarystat$Country2)
```

## Reviewer 2 requested analysis surrounding interaction between
## Objective SES and subjective SES in predicting SJ (Comment 4)
```{r}
regression3 <- lm(SJ ~ Eduaction_L1 + income_percent + Social_Status + Country2
                  + Eduaction_L1*Social_Status + income_percent*Social_Status +
                          Country2*Social_Status, data = finished_imputed_data)

summary(regression3)
anova(regression3)
```

## Exploring Region data per country
## Urban vs. Rural living
```{r}
library(tableone)
vars_for_table <- c("Country", "Urban_Rural")

CreateTableOne(vars = vars_for_table, data = D1_CHINA_AND_USA, strata = "Country")

```